\section*{Students and Postdoctoral Fellows Directly Supervised}
\begin{itemize}
  \item Mr. Rory Brown, University of St Andrews MPhys project; 2024-25 \\
  \emph{Neural Networks to Solve Radiative Transfer Problems in Protoplanetary Disks (Computation/Validation)}
  \item Mr. Patrick Connor, University of St Andrews BSc project; 2024-25\\
  \emph{Neural Networks to Solve Radiative Transfer Problems in Protoplanetary Disks (Theory/Exploration)}
  \item Mr. Brendan Murphy, University of St Andrews BSc project; 2024-25 \\
  \emph{Exploring Astrophysical Image Reconstruction Using the Scattering Transform}
  \item Ms. Mila Rollet De Fougerolles, University of St Andrews BSc project; 2023-24\\
  \emph{High Dimensional Parametric Models for Protoplanetary Disk Surface Brightness Modelling}
  \item Ms. Carol Ballinger, University of St Andrews MPhys project; 2023-24 \\
  \emph{Hierarchical Bayesian Modelling of Protoplanetary Disk Fractions Across Star Forming Regions}
  \item Ms. Marylyn Rosenqvist, University of St Andrews MPhys project; 2023-24 \\
  \emph{Mapping Kinematic Perturbations in Protoplanetary Disks Using Molecular Tracer HCN}
  \item Ms. Kristin Hopley, University of St Andrews MPhys project; 2023-24 \\
  \emph{Mapping the Inner Edge and Interior Cavity of a Kepler-Analog Circumbinary Protoplanetary
  Disk}
  \item Mr. Robert Frazier, Pennsylvania State University Undergraduate Student \\ 
  \emph{Regularized Maximum Likelihood Imaging for ALMA with \texttt{MPoL}}; Summer 2021
  \item Mr. Tyler Quinn, Pennsylvania State University Undergraduate Student \\ 
  \emph{Regularized Maximum Likelihood Imaging for ALMA with \texttt{MPoL}}; May 2021 - Dec 2021
  \item Ms. Hannah Grzybowski, Pennsylvania State University Undergraduate Student \\ 
  \emph{Regularized Maximum Likelihood Imaging for ALMA with \texttt{MPoL}}; May 2021 - Oct 2021
  \item Mr. Kadri Bin Mohamad Nizam, Pennsylvania State University Graduate Student \\ 
  \emph{Variational Autoencoders for Image Reconstruction of Protoplanetary Disks}; 2021 - present
  \item Dr. Brianna Zawadzki, Pennsylvania State University Ph.D. Thesis Advisor \\
  \emph{Regularized Maximum Likelihood Imaging for ALMA}; 2020 - 2023
  \item Ms. Zoe Ko, UC Berkeley Undergraduate Student \\ 
  \emph{Sub-Millimeter Selected Spectroscopic Binary Survey}; 2019 - 2022 
  \item Mr. Joseph Michael Akana Murphy, Stanford University Coterminal Masters Student \\
  Summer Research and Senior Thesis; 2017 - 2019\\
  \emph{Unveiling the Spectra of Young Stars with Gaussian Processes: Applications to LkCa~15}
  \item Dr. Jeff Jennings, Penn State University Eberly Postdoctoral Fellow \\
  Faculty Advisor, Aug 2022 - present\\
\end{itemize}
