\section*{Submitted Manuscripts}
\emph{\href{https://www.exoalma.com/}{exoALMA collaboration} first wave papers, submitted to The Astrophysical Journal Letters, Nov-Dec 2024}
\begin{enumerate}
\item Teague \emph{et al.} (incl \textbf{IC}), \emph{exoALMA I: Science Goals, Project Design and Data Products}
\item Loomis \emph{et al.} (incl \textbf{IC}), \emph{exoALMA II: Data Calibration and Imaging Pipeline}
\item Izquierdo \emph{et al.} (incl \textbf{IC}), \emph{exoALMA III: Line-intensity modelling and radial profile extraction from protoplanetary discs}
\item Curone \emph{et al.} (incl \textbf{IC}), \emph{exoALMA IV: Substructures, Asymmetries, and the Faint Outer Disk in Continuum Emission}
\item Galloway-Sprietsma \emph{et al.} (incl \textbf{IC}), \emph{exoALMA V: Emission Surfaces and Temperature Structures}
\item Stadler \emph{et al.} (incl \textbf{IC}), \emph{exoALMA VI: Rotating under Pressure Rotation curves, azimuthal velocity substructures and pressure variations}
\item Bae \emph{et al.} (incl \textbf{IC}), \emph{exoALMA VII. Benchmarking Hydrodynamics and Radiative Transfer Codes}
\item Hilder \emph{et al.} (incl \textbf{IC}), \emph{exoALMA VIII: Probabilistic super-resolution moment maps and data products using non-parametric linear models}
\item Zawadzki, Brianna; \textbf{Czekala, Ian}; \emph{et al.}, \emph{exoALMA IX: Regularized Maximum Likelihood Imaging of Non-Keplerian Features} (\textbf{significant mentorship role})
\item Pinte \emph{et al.} (incl \textbf{IC}), \emph{exoALMA X: channel maps reveal complex $^{12}$CO abundance distributions and a variety of kinematic structures with evidence for embedded planets}
\item Longarini \emph{et al.} (incl \textbf{IC}), \emph{exoALMA XII: Weighing and sizing exoALMA disks with rotation curve modelling}
\item Trapman \emph{et al.} (incl \textbf{IC}), \emph{exoALMA XIII. gas masses from N2H+ and C18O: a comparison of protoplanetary gas disk mass measurement techniques}
\item Rosotti \emph{et al.} (incl \textbf{IC}), \emph{exoALMA XV: Interpreting the height of CO emission layer}
\item Barraza-Afaro \emph{et al.} (incl \textbf{IC}), \emph{exoALMA XVI: Predicting signatures of large-scale turbulence in protoplanetary disks} 
\item W\"{o}lfer \emph{et al.} (incl \textbf{IC}), \emph{exoALMA XVII: Characterizing the Gas Dynamics Around Dust Asymmetries}
\end{enumerate}